IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-15 paper/formal.tex
progress noninter

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| satisfies termination
  sensitive non-interference if for any label |l|, and configurations
  $|c1, c1', c2|\in|C|$, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration $|c2'|\in|C|$ such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}
%
In other words, if we take two |l|-equivalent configurations, then for every
intermediate step taken by the first configuration, there is a corresponding
number of steps that the second configuration can take to result in a
configuration that is |l|-equivalent to the first resultant configuration.

Our IFC language satisfies TSNI %under a particular
%scheduling policy.
%
%Specifically, we consider the language
under the round-robin scheduler
|roundrobinf| given in Fig.~\ref{fig:scheduler}.

>>>>

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| satisfies termination
  sensitive non-interference if for any label |l|, and configurations
  $|c1, c1', c2|\in|C|$, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration $|c2'|\in|C|$ such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}
%
In other words, if we take two |l|-equivalent configurations, then for every
intermediate step taken by the first configuration, there is a corresponding
number of steps that the second configuration can take to result in a
configuration that is |l|-equivalent to the first resultant configuration.
By symmetry, this applies to all intermediate steps from the second configuration
as well.
%
We remark that this notion of non-interfernce is similar to
\emph{progress sensitive non-interference (PSNI)}, which accounts for
leakage via progress (or termination) channels, as used for static
systems~\cite{moore2012precise}.

Our IFC language satisfies TSNI 
(and thus PSNI)
under the round-robin scheduler
|roundrobinf| given in Fig.~\ref{fig:scheduler}.
